Covariates analysis of MSBB RNASeq data of region BM 36 (realigned from FASTQ extracted source BAM in minerva with STAR-HTSeq)

### 2016-09-20 code/Rmd/MSSM_BM_36_RNASeq_Realigned_StarHTSeq2.Rmd
Added markdown to process BM36 region from MSSM (started from source BAM in minerva converted to FASTQ using picard realigned using star and quantified using HTseq)

---
title: "Covariates analysis of MSBB RNASeq data of region BM 36 (realigned from source FASTQ with STAR-HTSeq)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(synapseClient)
library(knitr)
library(githubr)

@@

knit2synapse::knitToFolderEntity(file = "./MSSM_BM_36_RNASeq_Realigned_StarHTSeq.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB BM 36 RNASeq RealignedFromSource StarHTSeq')
```

@@

thisFileName <- 'MSSM_BM_36_RNASeq_Realigned_StarHTSeq.Rmd'

@@

Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
# Download expression data
COUNT_ID <- 'syn7224673'
ALL_USED_IDs <- COUNT_ID
COUNT <- read.table(synGet(COUNT_ID)@filePath, quote = '', header = T, sep = '\t')

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB BM 36 RNASeq  RealignedFromSource StarHTSeq", parentId = parentId)
CODE <- synStore(CODE)

@@

# Store differential expression results
write.table(DE, file = 'diffExpression.tsv', sep = '\t', row.names=F, quote=F)
dexp_obj = File('diffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
dexp_obj = synStore(dexp_obj, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
```
|  *Results*                |  *SynapseID*                    |
|  -------                  |   ---------                     |
|  Covariates               |  `r covar_obj$properties$id`    |
|  Residual Expression      |  `r expr_obj$properties$id`     |
|  Differential Expression  |  `r dexp_obj$properties$id`     |

>>>>

---
title: "Covariates analysis of MSBB RNASeq data of region BM 36 (realigned from FASTQ extracted source BAM in minerva with STAR-HTSeq)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(synapseClient)
library(knitr)
library(githubr)

@@

knit2synapse::knitToFolderEntity(file = "./MSSM_BM_36_RNASeq_Realigned_StarHTSeq2.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB BM 36 RNASeq RealignedFromSource BAM Picard StarHTSeq')
```

@@

thisFileName <- 'MSSM_BM_36_RNASeq_Realigned_StarHTSeq2.Rmd'

@@

Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
# Download expression data
COUNT_ID <- 'syn7254146'
ALL_USED_IDs <- COUNT_ID
COUNT <- read.table(synGet(COUNT_ID)@filePath, quote = '', header = T, sep = '\t')

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB BM 36 RNASeq RealignedFromSource BAM Picard StarHTSeq", parentId = parentId)
CODE <- synStore(CODE)

@@

# Store differential expression results
write.table(DE, file = 'diffExpression.tsv', sep = '\t', row.names=F, quote=F)
dexp_obj = File('diffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
dexp_obj = synStore(dexp_obj, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)

# Store logcpm values
write.table(VOOM.ADJUSTED.GENE_EXPRESSION$E, file = 'logCPM.tsv', sep = '\t', row.names=F, quote=F)
exp1_obj = File('logCPM.tsv', name = 'Raw logCPM', parentId = CODE$properties$id)
exp1_obj = synStore(exp1_obj, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

```
|  *Results*                |  *SynapseID*                    |
|  -------                  |   ---------                     |
|  Covariates               |  `r covar_obj$properties$id`    |
|  logCPM                   |  `r exp1_obj$properties$id`     |
|  Residual Expression      |  `r expr_obj$properties$id`     |
|  Differential Expression  |  `r dexp_obj$properties$id`     |
